### 2016-02-01 AcademicPaperSummaries/PaperSummaries.tex
Abrahms and half of Berrebi and Lackdawalla

\underline{Research question and research area:} Seems to speak most closely to the social capital literature and social determinants of political participation. 
\underline{Summary of argument and mechanism:} Mechanism is explicitly about information-sharing functions of social networks.
\underline{Data \& methods:} Survey data from 1984 Presidential election gathered in South Bend, Indiana. Unit of analysis is the discussion dyad. Dependent variable is a composite count of political activities beyond voting. Model is negative binomial regression.
\underline{Findings:} 
\underline{Notes on related papers:}
combining this article and the  Mutz findings and adding to the context  of social networks is interesting:
then we have a  clear vector of information (both  passive via FB  events) and active,  via people sharing  their views and  things like articles,  BUT also because some online social networks tend to be maximalist (especially Facebook) they also foster the  development of the type of cross- cutting networks that Mutz finds tends to make people cagy about political activism. I bet that beyond presidential election, social campaigns like support for Black Lives Matter would be a good test case of information sharing through networks (having partisans in online networks might increase access to POV and stories

@@

\underline{Research question and research area} Applying disaggregated data to underlying question of how terrorism influences voting patterns. \\
\underline{Definition of terrorism:} Terror attacks included if caused at least one non-combattant Israeli death.
\underline{Summary of argument and mechanism:} Terror attacks trigger residents of locality to alter their daily routine in response to perception of insecurity, (implied negative) influence on locality's economy and expected future income. These features antagonize the residents and makes them less supportive of concessions to Palestinian authority. Attacks in a locality also make the conflict more salient to residents of the locality [Note: not clear why this wouldn't be expected to apply to neighboring localities.]\\
\underline{Data \& methods:} Difference-in-difference. (Assumes that terror attacks are the only thing that differentiates patterns in voting across localities.) Dependent variable is vote share for political parties, for 1988, 1992, 1996, 199, and 2003. Terrorism measured via data on non-combattant Israeli fatalities from terror attacks.\\
\underline{Findings} Terrorism does cause polarization of the Israeli electorate, with a terror attack in a locality adding 1.35 percentage points to the locality's support for the political right.\\
\underline{Notes on related papers}\\

>>>>

\underline{Research question and research area:} Seems to speak most closely to the social capital literature and social determinants of political participation. 
\underline{Summary of argument and mechanism:} Mechanism is explicitly about information-sharing functions of social networks.
\underline{Data \& methods:} Survey data from 1984 Presidential election gathered in South Bend, Indiana. Unit of analysis is the discussion dyad. Dependent variable is a composite count of political activities beyond voting. Model is negative binomial regression.
\underline{Findings:} 
\underline{Notes on related papers:}
combining this article and the  Mutz findings and adding to the context  of social networks is interesting:
then we have a  clear vector of information (both  passive via FB  events) and active,  via people sharing  their views and  things like articles,  BUT also because some online social networks tend to be maximalist (especially Facebook) they also foster the  development of the type of cross- cutting networks that Mutz finds tends to make people cagy about political activism. I bet that beyond presidential election, social campaigns like support for Black Lives Matter would be a good test case of information sharing through networks (having partisans in online networks might increase access to POV and stories.

\textbf{Nickerson, David W. 2008. “Is Voting Contagious? Evidence from Two Field Experiments.”
American Political Science Review 102(1): 49–57.}

\underline{Keywords:} voting behavior, networks
\underline{Research question and research area} This article is looking at testing one of the mechanisms behind why spouses exhibit similar behavior: whether they converge together or pre-select for similarity.\\
\underline{Summary of argument and mechanism} Network mechanism being tested is information exchange through strong ties.\\
\underline{Data \& methods} Experiments in Denver, Co and Minneapolis, MN for 2002 congressional primaries.\\
\underline{Findings} Canvassing resulted in an 8\% increase in propensity to vote among contacted people, and a 5.5 (CO) and 6.5\% (MN) increase among cohabitants of the person contacted. Wording is vague, bit it looks l ike significance didn't meet .05 threshold but did meet .1\\
\underline{Notes on related papers} They're using ``spouse'' and ``roommate'' interchangeably in their mechanism description. This implies that the mechanism is supposed to be just information exchange, particularly in an environment of strong ties, vs pressures driving spouses to similarity.   \\

\textbf{Lazer, David, Katya Ognyanova, William Minozzi, and Michael Neblo. “The social control of
political participation: Conflict and contagion as processes (de)mobilizing voting.” Working Paper.}

\underline{Keywords:} mechanism testing

\underline{Research question and research area} The paper tries to test the contagion and conflict mechanisms of network effects on voting behavior\\
\underline{Summary of argument and mechanism} No proposed mechanism, trying to experimentally test debate in literature about whether conflict or contagion effects are at work in networks of undergrads\\
\underline{Data \& methods} Data is from 14 dorms in election years from 2008-2012\\
\underline{Findings} Findings support contagion, although I suspect that their survey question doesn't quite parse out the question of whether people frequently talk about politics with those whom they disagree. \\
\underline{Notes on related papers}\\

@@

\underline{Research question and research area} Applying disaggregated data to underlying question of how terrorism influences voting patterns. \\
\underline{Definition of terrorism:} Terror attacks included if caused at least one non-combattant Israeli death.
\underline{Summary of argument and mechanism:} Terror attacks trigger residents of locality to alter their daily routine in response to perception of insecurity, (implied negative) influence on locality's economy and expected future income. These features antagonize the residents and makes them less supportive of concessions to Palestinian authority. Attacks in a locality also make the conflict more salient to residents of the locality [Note: not clear why this wouldn't be expected to apply to neighboring localities.]\\
\underline{Data \& methods:} Difference-in-difference. (Assumes that terror attacks are the only thing that differentiates patterns in voting across localities.) Dependent variable is vote share for political parties, for 1988, 1992, 1996, 199, and 2003. Terrorism measured via data on non-combattant Israeli fatalities from terror attacks.\\
\underline{Findings} Terrorism does cause polarization of the Israeli electorate, with a terror attack in a locality adding 1.35 percentage points to the locality's support for the political right.\\
\underline{Notes on related papers} Note that this study shares the general problem of the artificiality of borders for some kinds of questions. See also the Condra and Shapiro ``who takes the blame'' article. \\

\textbf{Condra, Luke. N. and Jacob N. Shapiro. 2012. “Who Takes the Blame? The Strategic E↵ects
of Collateral Damage.” American Journal of Political Science 56 (1): 167-187.}

\underline{Research question and research area}\\
\underline{Summary of argument and mechanism} Civilians are strategic agents, who will provide information on insurgents whom they are dissatisfied with, when insurgents kill civilians the civilians provide more information to the state. Note that they do not include ``intimidation killings'' in their data, which seems like an important omission when talking about civilian decisions about whether to provide information--- intimidation should drive down all reporting to Coalitions.  \\
\underline{Data \& methods} Daily trends in battlefield violence in Iraq from February 2004 through February 2009. Deaths from the Iraq Body Count, attacks from the MNF-I SIGACTS III database at the Empirical Studies of Conflict. Unit of analysis is district-week. \\
\underline{Findings} Find that insurgents and coalition forces pay penalties for violence against civilians- but unevenly throughout the country. The effect is strongest in urban environments.\\
\underline{Notes on related papers} (From Problems in IR reading)Kocher, Shapiro, Condra: focus on rational peasant model (Popkins) vs Lyall's work in Chechnya that has tended to view state forces as the active agents.\\

\textbf{Fortna, Virginia Page. 2015. “Do Terrorists Win? Rebels’ Use of Terrorism and Civil War
Outcomes.” International Organization 69(3): 519-556.}

\underline{Research question and research area} Fortna's research question, ``how effective is terrorism,'' places her in the literature on effectiveness of terrorism. (Lit review on pp 521:522 has nice overview of the pro/con sides of whether terrorism is effective)\\
\underline{Implied/Stated model of terrorism:} Defines terrorist rebel groups as one that ``uses a systemic campaign of indiscriminate violence against public civilian targets to influence a wider audience'' (pg 523). Observe that this definition misses the norm-violating attribute that other thinkers, such as Crenshaw, include. This relies heavily on Jessica Stanton's typology and coding of terrorism.\\
\underline{Summary of argument and mechanism} Assumes that all agents are participating in a civil war, and have a hierarchy of preferred outcomes of the war with rebel victory $>$ negotiated settlement $>$ fizzle out $>$ government victory (worst)  \\
\underline{Data \& methods} Data is restricted to civil wars\\
\underline{Findings} Terrorism undermines effectiveness in concessions and bargaining, less bad against democracies but still never effective; wars with terrorism are longer wars thus suggesting that terrorism is effective as a tool for organizational survival.\\
\underline{Notes on related papers}\\

Terrorism week 7\\

\textbf{Bueno de Mesquita, Ethan and Eric Dickson. 2007. “The Propaganda of the Deed: Terrorism,
Counterterrorism, and Moblization.” American Journal of Political Science 51(2).}
